---
title: "Getting Started with bibnets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with bibnets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bibnets)
```

## Datasets

This vignette uses two datasets:

- **`scopus_quantum_cloud`** — 499 Scopus records on green cloud computing and
  quantization (2020–2025), with author keywords and affiliations. Source:
  Elsevier Scopus, archived at
  [doi:10.5281/zenodo.17142636](https://doi.org/10.5281/zenodo.17142636) (CC BY 4.0).
- **`open_alex_gold_open_access_learning_analytics`** — 1,508 gold open-access
  works on learning analytics from OpenAlex (CC0), with authors, countries, and
  institutions.

```{r}
data(scopus_quantum_cloud)
data(open_alex_gold_open_access_learning_analytics)

sc  <- scopus_quantum_cloud
oa  <- open_alex_gold_open_access_learning_analytics
```

## Reading data

`read_biblio()` auto-detects the format of your export file:

```{r, eval = FALSE}
data <- read_biblio("export.csv")          # Scopus, WoS, Dimensions, Lens, OpenAlex
data <- read_biblio("refs.bib")            # BibTeX
data <- read_biblio("refs.ris")            # RIS

# Or call the format-specific readers directly:
data <- read_scopus("scopus.csv")
data <- read_wos("savedrecs.txt")
data <- read_openalex_csv("works.csv")
data <- read_dimensions("dims.csv")
data <- read_lens("lens.csv")
```

The bundled dataset can also be read directly from the archived CSV:

```{r, eval = FALSE}
sc <- read_scopus("scopus_quantum_cloud.csv")
```

All readers return the same standard column set: `id`, `title`, `year`,
`journal`, `doi`, `cited_by_count`, `abstract`, `type`, plus list-columns
`authors`, `references`, and `keywords`.

## Author, country, and institution collaboration

Authors, countries, and institutions are all facets of the same authorship
record, so they are naturally demonstrated together. The OpenAlex dataset is
used here: it is large enough (1,508 papers) to produce meaningful networks
and already carries `countries` and `affiliations` columns.

### Authors

Two authors are linked when they co-author at least one publication.

```{r}
collab <- author_network(oa, "collaboration")
collab
```

Keep only the strongest collaborations:

```{r}
prune(collab, threshold = 3)
```

Fractional counting down-weights authors on large teams:

```{r}
author_network(oa, "collaboration", counting = "fractional")
```

### Countries

Two countries are linked when authors from both appear on the same paper.
Fractional counting normalizes by collaboration size so that large multi-author
papers do not dominate the network.

```{r}
country_network(oa, "collaboration", counting = "fractional")
```

### Institutions

```{r}
institution_network(oa, "collaboration", counting = "fractional")
```

## Keyword co-occurrence

Two keywords are linked when they appear together in the same paper.

```{r}
kw <- keyword_network(sc)
kw
```

## Counting methods

bibnets implements 13 counting methods. The first four are
**position-independent** and work for all network types. The remaining nine are
**position-dependent** and apply fractional credit based on byline order
(collaboration networks only).

| Method | Description |
|---|---|
| `"full"` | Each co-occurrence counts as 1 |
| `"fractional"` | Weight = 1 / (k_i × k_j) |
| `"paper"` | Weight = 1 / k_i (paper normalised) |
| `"strength"` | IDF-weighted / (k_i × k_j) (Perianes-Rodriguez 2016) |
| `"harmonic"` | Credit ∝ 1/position (Hagen 2008) |
| `"arithmetic"` | Credit ∝ (n − pos + 1) / sum |
| `"geometric"` | Credit ∝ 2^(n − pos) / sum (Liu & Fang 2023) |
| `"adaptive_geometric"` | Geometric, adapted to author count |
| `"golden"` | Credit ∝ φ^(n − pos) |
| `"first"` | Credit = 1 for first author, 0 for others |
| `"last"` | Credit = 1 for last author, 0 for others |
| `"first_last"` | First and last authors upweighted |
| `"position_weighted"` | Custom weight vector |

```{r}
# Harmonic counting rewards first authorship
author_network(oa, "collaboration", counting = "harmonic")
```

## Reducing networks

### Backbone extraction (Serrano disparity filter)

The disparity filter retains edges that are statistically significant for at
least one endpoint — preserving multiscale structure rather than applying a
global threshold.

```{r}
edges <- author_network(oa, "collaboration")
backbone(edges, alpha = 0.05)
```

### Pruning

```{r}
edges <- keyword_network(sc)

# Remove weak edges
prune(edges, threshold = 2)

# Top-k neighbours per node
prune(edges, top_n = 3)
```

### Top nodes

```{r}
filter_top(edges, n = 10)
```

## Temporal networks

`temporal_network()` wraps any builder over time windows. The OpenAlex dataset
spans multiple years and is used here.

```{r}
# Fixed 3-year windows
tn <- temporal_network(oa, author_network, "collaboration", window = 3)
names(tn)

# Each element is a standard bibnets_network
tn[[1]]

# Cumulative windows — each period includes all prior papers
temporal_network(oa, author_network, "collaboration",
                 window = 3, strategy = "cumulative")
```

## Generic conetwork

`conetwork()` builds any co-occurrence or bipartite-projected network from any
column, without a dedicated function:

```{r}
# Keywords co-occurring in the same paper
conetwork(sc, "keywords")

# Authors linked by shared keywords
conetwork(sc, "authors", by = "keywords")
```

## Exporting networks

```{r}
edges <- keyword_network(sc)

# Sparse adjacency matrix
m <- to_matrix(edges)
m[1:4, 1:4]

# Gephi node/edge tables (pass file = "dir/" to write CSVs)
gephi <- to_gephi(edges)
head(gephi$edges)

# GraphML string (pass file = "out.graphml" to write)
xml <- to_graphml(edges)
cat(substr(xml, 1, 300))

# igraph (requires igraph package)
# g <- to_igraph(edges)

# cograph (requires cograph package)
# net <- to_cograph(edges)
```

## S3 methods

All network functions return a `bibnets_network` object — a data frame subclass
carrying metadata as attributes.

```{r}
edges <- author_network(oa, "collaboration", counting = "harmonic")

print(edges)
summary(edges)

attr(edges, "network_type")
attr(edges, "counting")
```
