---
title: "Getting Started with citenets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with citenets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(citenets)
data(biblio_data)
```

## Reading data

citenets reads all major bibliometric formats. Auto-detect with `read_biblio()`:

```{r, eval = FALSE}
data <- read_biblio("export.csv")       # Scopus, WoS, Dimensions, Lens, BibTeX, RIS
data <- read_scopus("scopus.csv")       # Scopus CSV
data <- read_wos("savedrecs.txt")       # Web of Science full-record export
data <- read_openalex("works.csv")      # OpenAlex CSV download
data <- read_lens("lens.csv")           # Lens.org CSV export
data <- read_bibtex("refs.bib")         # BibTeX file
data <- read_ris("refs.ris")            # RIS file
data <- read_dimensions("dims.csv")     # Dimensions CSV
```

## Building networks

### Author networks

```{r}
# Co-authorship with full counting (default)
collab <- author_network(biblio_data, "collaboration")
collab

# Harmonic counting — downweights non-first authors
author_network(biblio_data, "collaboration", counting = "harmonic")

# Bibliographic coupling — authors who cite the same references
author_network(biblio_data, "coupling")
```

### Keyword co-occurrence

```{r}
kw <- keyword_network(biblio_data)
kw

# With association strength normalization
keyword_network(biblio_data, similarity = "association")
```

### Document networks

```{r}
# Bibliographic coupling
document_network(biblio_data, "coupling")

# Co-citation
document_network(biblio_data, "co_citation")

# Direct citation (directed edges, internal only)
document_network(biblio_data, "citation")
```

### Reference co-citation

```{r}
reference_network(biblio_data, similarity = "association")
```

### Source, country, institution

```{r, eval = FALSE}
source_network(data, "coupling")
country_network(data, "collaboration")
institution_network(data, "collaboration")
```

### Generic conetwork

`conetwork()` builds any co-occurrence or bipartite-projected network from
any column without a pre-defined function:

```{r}
# Keywords appearing in the same document
conetwork(biblio_data, "keywords")

# Authors linked by shared keywords
conetwork(biblio_data, "authors", by = "keywords")

# Works with semicolon-delimited string columns too
d <- data.frame(id = 1:3, tags = c("ml; dl", "ml; nlp", "dl; nlp"))
conetwork(d, "tags")
```

## Counting methods

citenets implements 13 counting methods. The first 4 are
**position-independent** and work for all network types. The remaining 9 are
**position-dependent** and apply fractional credit based on byline order
(collaboration networks only).

| Method | Description |
|---|---|
| `"full"` | Each co-occurrence counts as 1 |
| `"fractional"` | Weight = 1 / (k_i × k_j) |
| `"paper"` | Weight = 1 / k_i (paper normalised) |
| `"strength"` | Weight = 1 / k |
| `"harmonic"` | Credit ∝ 1/position (Hagen 2008) |
| `"arithmetic"` | Credit ∝ (n − pos + 1) / sum |
| `"geometric"` | Credit ∝ 2^(n − pos) / sum (Liu & Fang 2023) |
| `"adaptive_geometric"` | Geometric, adapted to author count |
| `"golden"` | Credit ∝ φ^(n − pos) |
| `"first"` | Credit = 1 for first author, 0 for others |
| `"last"` | Credit = 1 for last author, 0 for others |
| `"first_last"` | First and last authors upweighted |
| `"position_weighted"` | Custom weight vector |

```{r}
author_network(biblio_data, "collaboration", counting = "geometric")
author_network(biblio_data, "collaboration", counting = "first_last",
               first_last_weight = 2)
```

## Similarity (normalization) measures

```{r}
# Association strength (van Eck & Waltman 2009)
keyword_network(biblio_data, similarity = "association")

# Salton cosine
keyword_network(biblio_data, similarity = "cosine")

# Jaccard, inclusion, equivalence also available
keyword_network(biblio_data, similarity = "jaccard")
```

## Reducing networks

### Backbone extraction (Serrano disparity filter)

The disparity filter keeps edges that are statistically significant for at
least one of their endpoints — preserving the multiscale structure of weighted
networks rather than cutting by a global threshold.

```{r}
edges <- author_network(biblio_data, "collaboration")
backbone(edges, alpha = 0.05)
```

### Pruning

```{r}
edges <- keyword_network(biblio_data)

# Global weight threshold
prune(edges, method = "threshold", value = 2)

# Top-k neighbours per node
prune(edges, method = "top_n", value = 3)
```

### Filter to top nodes

```{r}
filter_top(edges, n = 5)
```

## Temporal networks

```{r}
# Fixed 3-year windows
tn <- temporal_network(biblio_data, author_network, "collaboration", window = 3)
names(tn)

# Each element is a standard edge data frame
if (length(tn) > 0) tn[[1]]

# Cumulative windows
temporal_network(biblio_data, keyword_network, window = 2,
                 strategy = "cumulative")
```

## Historiograph

The historiograph shows which locally cited documents cite each other,
laid out chronologically — the classic Garfield citation history.

```{r}
h <- historiograph(biblio_data, n = 10, min_lcs = 1)

# Node table: top-cited documents with metadata
head(h$nodes)

# Edge table: directed citation links
head(h$edges)

# Local citation scores for the full dataset
head(local_citations(biblio_data))
```

## Exporting networks

```{r}
edges <- keyword_network(biblio_data)

# Adjacency matrix
m <- to_matrix(edges)
m[1:4, 1:4]

# Gephi (returns list; pass file = "dir/" to write CSVs)
gephi <- to_gephi(edges)
head(gephi$edges)

# GraphML string (pass file = "out.graphml" to write)
xml <- to_graphml(edges)
cat(substr(xml, 1, 200))

# igraph (requires igraph package)
# g <- to_igraph(edges)

# cograph (requires cograph package)
# net <- to_cograph(edges)
```

## S3 methods

All network functions return a `citenets_network` object — a data frame
subclass that carries metadata as attributes.

```{r}
edges <- author_network(biblio_data, "collaboration", counting = "harmonic")

# Print shows a summary header
print(edges)

# Summary shows network statistics
summary(edges)

# Metadata accessible via attr()
attr(edges, "network_type")
attr(edges, "counting")
```
