---
title: "citenets: Citation and Bibliometric Network Construction in R"
subtitle: "A Comprehensive Tutorial with Equivalence Testing"
author: "Mohammed Saqr"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    code-tools: true
    theme: flatly
    fig-width: 7
    fig-height: 5
execute:
  warning: false
  message: false
---

## 1. Why citenets?

Bibliometric network analysis requires constructing networks from scholarly data — who collaborates with whom, which papers are cited together, what keywords co-occur. Existing tools either bundle everything into a monolithic package with 87+ dependencies (bibliometrix) or cover only fragments of the problem (biblionetwork).

citenets fills the gap: **network construction only**, with state-of-the-art counting and normalization methods, minimal dependencies, and an intuitive API.

| Feature | citenets | bibliometrix | biblionetwork |
|---------|----------|--------------|---------------|
| **Counting methods** | 13 | 1 (full) | 3 |
| **Similarity measures** | 6 | 5 | 1 (cosine) |
| **Network types** | 8 functions | 4 | 3 |
| **Dependencies** | 3 | 87+ | 3 |
| **Output** | Data frame | Sparse matrix | Data table |

```{r}
#| label: setup
devtools::load_all("..")
```

## 2. Reading Bibliometric Data

citenets reads data from six sources into a unified tidy format: every reader returns the same column structure with human-readable names and list-columns for multi-valued fields.

### 2.1 From Scopus CSV

```{r}
#| label: read-scopus
data(biblio_data)
str(biblio_data, max.level = 1)
```

The standardized format: `id`, `title`, `year`, `journal`, `doi`, `cited_by_count` as scalars. `authors`, `references`, `keywords` as list-columns — already split, no semicolons to wrestle with.

```{r}
#| label: show-authors
# Each paper's authors are a character vector, not a semicolon string
biblio_data$authors[[1]]
```

### 2.2 Other Formats

All readers return the same structure:

```r
# Web of Science plaintext
data <- read_wos("savedrecs.txt")

# Web of Science tab-delimited
data <- read_wos("savedrecs.txt", format = "tab")

# OpenAlex (from openalexR::oa_fetch output)
data <- read_openalex(oa_results)

# BibTeX (note: no cited references in standard .bib)
data <- read_bibtex("refs.bib")

# RIS (note: no cited references in standard .ris)
data <- read_ris("export.ris")

# Lens.org CSV
data <- read_lens("lens_export.csv")
```

## 3. Network Types

citenets builds seven types of entity networks plus a generic co-occurrence function.

### 3.1 Author Collaboration Network

Two authors are linked when they co-author a paper. The most common bibliometric network.

```{r}
#| label: author-collab
edges <- author_network(biblio_data, "collaboration")
edges
```

Each row is an edge. `weight` = co-authorship count, `count` = raw count, `shared` = number of shared papers.

### 3.2 Reference Co-citation Network

Two references are linked when they are cited together by the same paper. Co-citation strength reflects intellectual structure — which foundational works are perceived as related.

```{r}
#| label: ref-cocit
edges <- reference_network(biblio_data, threshold = 0)
head(edges, 10)
```

### 3.3 Document Bibliographic Coupling

Two documents are linked when they share cited references. Unlike co-citation (retrospective), coupling is prospective — computable immediately upon publication.

```{r}
#| label: doc-coupling
edges <- document_network(biblio_data, "coupling")
head(edges)
```

### 3.4 Direct Citation Network

Directed edges from citing to cited documents. Only internal citations (both documents present in the dataset) are included.

```{r}
#| label: direct-cit
edges <- document_network(biblio_data, "citation")
edges
```

### 3.5 Keyword Co-occurrence Network

Two keywords are linked when they appear in the same paper.

```{r}
#| label: keyword-cooc
edges <- keyword_network(biblio_data, threshold = 0)
head(edges, 10)
```

### 3.6 Other Entity Networks

Institution, country, and source (journal) networks follow the same pattern:

```r
# Institutions linked by co-authorship
institution_network(data, "collaboration")

# Countries linked by shared references
country_network(data, "coupling")

# Journals linked by co-citation
source_network(data, "co_citation")
```

Each supports types: `"collaboration"`, `"coupling"`, `"co_citation"`, `"equivalence"` (where applicable).

## 4. Counting Methods — The Core Innovation

Counting methods determine how credit is distributed among co-authors or how co-occurrences are weighted. citenets implements 13 methods — 9 more than any other R package.

### 4.1 Position-Independent Methods (4)

These treat all authors equally regardless of byline position.

```{r}
#| label: counting-independent
d <- data.frame(id = "W1", stringsAsFactors = FALSE)
d$authors <- list(c("Alice", "Bob", "Carol"))

# Full counting: each link = 1
author_network(d, "collaboration", counting = "full")

# Fractional (Perianes-Rodriguez): each author's total = 1
# Link weight = 1/(n-1) = 0.5
author_network(d, "collaboration", counting = "fractional")

# Paper-level fractional (Batagelj): paper total = 1
# Link weight = 2/(n*(n-1)) = 1/3
author_network(d, "collaboration", counting = "paper")
```

The difference: **fractional** normalizes per author (each author's total co-authorship from this paper = 1). **Paper** normalizes per paper (the paper's total contribution to the network = 1).

```{r}
#| label: counting-paper-verify
# Verify Batagelj property: total contribution per paper = 1
edges <- author_network(d, "collaboration", counting = "paper")
sum(edges$weight)  # Should be 1.0
```

### 4.2 Position-Dependent Methods (9)

These respect author byline order — first author gets more credit.

```{r}
#| label: counting-weights
# Compare all position-dependent methods for a 5-author paper
methods <- c("harmonic", "arithmetic", "geometric",
             "adaptive_geometric", "golden",
             "first", "last", "first_last")

weights_table <- do.call(rbind, lapply(methods, function(m) {
  w <- author_weights(5, m)
  data.frame(method = m, pos1 = w[1], pos2 = w[2], pos3 = w[3],
             pos4 = w[4], pos5 = w[5])
}))
weights_table
```

#### Harmonic (Hagen 2008)

Credit proportional to 1/position. The first author always gets twice the credit of the second, the second 1.5 times the third, etc.

```{r}
#| label: harmonic
author_network(biblio_data, "collaboration", counting = "harmonic") |>
  head(5)
```

#### Geometric

Exponential decay: 0.5^(position-1). Concentrates credit heavily on early authors.

```{r}
#| label: geometric
author_network(biblio_data, "collaboration", counting = "geometric") |>
  head(5)
```

#### Adaptive Geometric (Liu & Fang 2023)

The ratio of first to last author credit equals the number of authors. Adapts to team size.

```{r}
#| label: adaptive
# Verify: first/last ratio = n
for (n in c(3, 5, 10)) {
  w <- author_weights(n, "adaptive_geometric")
  cat(sprintf("n=%2d: first/last = %.2f (expected %d)\n", n, w[1]/w[n], n))
}
```

#### Golden Ratio

Uses phi (1.618...) as the decay constant. Consecutive authors have a ratio of phi.

```{r}
#| label: golden
w <- author_weights(5, "golden")
phi <- (1 + sqrt(5)) / 2
cat("Consecutive ratios:", paste(round(w[1:4] / w[2:5], 3), collapse = ", "), "\n")
cat("Expected phi:", round(phi, 3), "\n")
```

#### First / Last / First-Last

```{r}
#| label: first-last
# First author only: others get zero weight → no co-authorship edges
author_weights(4, "first")

# Last author only
author_weights(4, "last")

# First and last elevated, middle share rest
author_weights(4, "first_last")
```

#### Position Weighted (custom)

User-defined weight vector:

```{r}
#| label: position-weighted
# Custom: heavy first, moderate second, equal rest
author_network(biblio_data, "collaboration",
               counting = "position_weighted",
               position_weights = c(1.0, 0.7, 0.3))  |>
  head(5)
```

### 4.3 How Position-Dependent Counting Affects Network Edges

The key mechanism: author positional weights are placed directly into the bipartite matrix. Matrix multiplication then gives edge weight = w_i * w_j per shared paper. Higher-ranked author pairs get stronger edges.

```{r}
#| label: counting-mechanism
# One paper: Alice (pos 1), Bob (pos 2), Carol (pos 3)
d <- data.frame(id = "W1", stringsAsFactors = FALSE)
d$authors <- list(c("Alice", "Bob", "Carol"))

# Harmonic weights: Alice = 6/11, Bob = 3/11, Carol = 2/11
w <- author_weights(3, "harmonic")
cat("Weights:", round(w, 4), "\n")

# Edge weight = product of positional weights
edges <- author_network(d, "collaboration", counting = "harmonic")
cat("Alice-Bob:", round(w[1] * w[2], 4), "=", round(edges$weight[edges$from == "Alice" & edges$to == "Bob"], 4), "\n")
cat("Alice-Carol:", round(w[1] * w[3], 4), "=", round(edges$weight[edges$from == "Alice" & edges$to == "Carol"], 4), "\n")
cat("Bob-Carol:", round(w[2] * w[3], 4), "=", round(edges$weight[edges$from == "Bob" & edges$to == "Carol"], 4), "\n")
```

## 5. Similarity Measures

After counting co-occurrences, similarity measures normalize edge weights to account for how active each entity is. An entity that appears in 100 papers will naturally co-occur with more entities — normalization corrects for this.

### 5.1 The Six Measures

Given co-occurrence count c_ij and total occurrences w_i, w_j:

| Similarity | Formula | When to use |
|------------|---------|-------------|
| `"none"` | c_ij | Raw counts, no correction |
| `"association"` | c_ij / (w_i * w_j) | Recommended default (van Eck & Waltman 2009) |
| `"cosine"` | c_ij / sqrt(w_i * w_j) | Coupling angle (Sen & Gan 1983) |
| `"jaccard"` | c_ij / (w_i + w_j - c_ij) | Set overlap |
| `"inclusion"` | c_ij / min(w_i, w_j) | Subset detection |
| `"equivalence"` | c_ij^2 / (w_i * w_j) | Cosine squared |

```{r}
#| label: similarity-compare
# Same network, different similarity measures
methods <- c("none", "association", "cosine", "jaccard", "inclusion", "equivalence")

results <- lapply(methods, function(m) {
  e <- reference_network(biblio_data, similarity = m, threshold = 0)
  data.frame(similarity = m,
             edges = nrow(e),
             min_weight = round(min(e$weight), 4),
             max_weight = round(max(e$weight), 4),
             mean_weight = round(mean(e$weight), 4))
})
do.call(rbind, results)
```

### 5.2 Association Strength — The Recommended Default

Association strength measures how much more often two entities co-occur than expected by chance. A value of 1 means exactly as expected; >1 means they co-occur more than random; <1 means less.

```{r}
#| label: association
edges <- reference_network(biblio_data, similarity = "association", threshold = 0)
head(edges)
```

### 5.3 Cosine Similarity = Coupling Angle

For bibliographic coupling, cosine normalization is equivalent to the "coupling angle" of Sen & Gan (1983).

```{r}
#| label: cosine-coupling
# Document coupling with cosine = coupling angle
edges <- document_network(biblio_data, "coupling", similarity = "cosine")
head(edges)
```

## 6. The Generic conetwork Function

`conetwork()` works with **any data frame** — no `read_scopus()` required. Point it at a column and go.

### 6.1 Basic Co-occurrence

```{r}
#| label: conetwork-basic
# Any data frame with a delimited column
df <- data.frame(
  id = 1:5,
  tags = c("ml; dl; nlp", "ml; cv", "dl; nlp; cv",
           "stats; ml; regression", "dl; cv; stats"),
  year = c(2020, 2020, 2021, 2021, 2022)
)

conetwork(df, "tags", sep = ";")
```

### 6.2 Linked By Another Field

```{r}
#| label: conetwork-by
# Tags linked through shared categories
df$category <- c("A", "A", "B", "B", "A")
conetwork(df, "tags", by = "category", sep = ";")
```

### 6.3 Works With List-Columns Too

```{r}
#| label: conetwork-list
# Already-split list-columns: set sep = NULL
conetwork(biblio_data, "keywords", sep = NULL)  |> head()
```

### 6.4 On Raw Scopus Data (No Preprocessing)

```r
# Read raw CSV — don't use read_scopus(), just read.csv()
raw <- read.csv("scopus_export.csv")

# Build network directly from the raw column names
conetwork(raw, "Author.Keywords", sep = ";")
conetwork(raw, "Authors", sep = ",")
conetwork(raw, "Authors", by = "Author.Keywords", sep = ";")
```

## 7. Converters

Network edges go anywhere — igraph, tidygraph, or back to a matrix.

```{r}
#| label: converters
edges <- author_network(biblio_data, "collaboration")

# To igraph
g <- to_igraph(edges)
cat("igraph:", igraph::vcount(g), "nodes,", igraph::ecount(g), "edges\n")

# To adjacency matrix
A <- to_matrix(edges)
cat("Matrix:", nrow(A), "x", ncol(A), "\n")
```

```r
# To tidygraph (requires tidygraph package)
tg <- to_tbl_graph(edges)
```

## 8. Equivalence Testing — citenets vs bibliometrix vs biblionetwork

The following sections verify that citenets produces numerically identical results to established packages.

### 8.1 Co-authorship: citenets vs bibliometrix

```{r}
#| label: equiv-coauth-bm
library(bibliometrix)

# Same data in both formats
d_cn <- data.frame(id = paste0("W", 1:5), stringsAsFactors = FALSE)
d_cn$authors <- list(
  c("SMITH J", "JONES A", "LEE K"),
  c("SMITH J", "BROWN M"),
  c("JONES A", "LEE K", "CHEN W"),
  c("BROWN M", "DAVIS R", "SMITH J"),
  c("LEE K", "CHEN W")
)

M_bm <- data.frame(
  AU = c("SMITH J;JONES A;LEE K", "SMITH J;BROWN M",
         "JONES A;LEE K;CHEN W", "BROWN M;DAVIS R;SMITH J",
         "LEE K;CHEN W"),
  DB = rep("ISI", 5), stringsAsFactors = FALSE
)

# citenets
A_cn <- as.matrix(to_matrix(author_network(d_cn, "collaboration")))

# bibliometrix
A_bm <- as.matrix(biblioNetwork(M_bm, analysis = "collaboration", network = "authors"))
diag(A_bm) <- 0

# Align and compare
common <- sort(intersect(rownames(A_cn), rownames(A_bm)))
max_diff <- max(abs(A_cn[common, common] - A_bm[common, common]))
cat("Max difference:", max_diff, "\n")
```

### 8.2 Co-authorship Full Counting: citenets vs biblionetwork

```{r}
#| label: equiv-coauth-full
library(biblionetwork)
library(data.table)

auth_long <- data.table(
  article = c("W1","W1","W1", "W2","W2", "W3","W3","W3"),
  author  = c("A","B","C",    "A","B",    "B","C","D")
)
d <- data.frame(id = c("W1", "W2", "W3"), stringsAsFactors = FALSE)
d$authors <- list(c("A","B","C"), c("A","B"), c("B","C","D"))

# biblionetwork
bn <- as.data.frame(coauth_network(auth_long, authors = "author",
                                    articles = "article", method = "full_counting"))
# citenets
cn <- author_network(d, "collaboration", counting = "full")

# Compare
comparison <- merge(
  cn[, c("from", "to", "weight")],
  bn[, c("from", "to", "weight")],
  by = c("from", "to"), suffixes = c(".citenets", ".biblionetwork")
)
if (nrow(comparison) == 0) {
  bn2 <- bn; names(bn2)[1:2] <- c("to", "from")
  comparison <- merge(cn[, c("from","to","weight")], bn2[, c("from","to","weight")],
                      by = c("from","to"), suffixes = c(".citenets", ".biblionetwork"))
}
comparison$diff <- comparison$weight.citenets - comparison$weight.biblionetwork
comparison
```

### 8.3 Fractional Counting: citenets vs biblionetwork

```{r}
#| label: equiv-fractional
# biblionetwork fractional = 1/(n-1) per link = Perianes-Rodriguez
bn_frac <- as.data.frame(coauth_network(auth_long, authors = "author",
                                         articles = "article",
                                         method = "fractional_counting"))
cn_frac <- author_network(d, "collaboration", counting = "fractional")

cat("=== biblionetwork (fractional_counting) ===\n")
print(bn_frac[, c("from", "to", "weight")])
cat("\n=== citenets (counting = 'fractional') ===\n")
print(cn_frac[, c("from", "to", "weight")])
```

### 8.4 Paper-Level Fractional: citenets vs biblionetwork

```{r}
#| label: equiv-paper
# biblionetwork fractional_counting_refined = 2/(n*(n-1)) = Batagelj
bn_ref <- as.data.frame(coauth_network(auth_long, authors = "author",
                                        articles = "article",
                                        method = "fractional_counting_refined"))
cn_paper <- author_network(d, "collaboration", counting = "paper")

cat("=== biblionetwork (fractional_counting_refined) ===\n")
print(bn_ref[, c("from", "to", "weight")])
cat("\n=== citenets (counting = 'paper') ===\n")
print(cn_paper[, c("from", "to", "weight")])
```

### 8.5 Coupling Cosine: citenets vs biblionetwork

```{r}
#| label: equiv-coupling
refs_long <- data.table(
  citing = c("W1","W1","W1", "W2","W2","W2", "W3","W3","W3"),
  cited  = c("R1","R2","R3", "R1","R2","R4", "R2","R3","R4")
)
d_refs <- data.frame(id = c("W1","W2","W3"), stringsAsFactors = FALSE)
d_refs$references <- list(c("R1","R2","R3"), c("R1","R2","R4"), c("R2","R3","R4"))

# biblionetwork: coupling angle (cosine)
bn_coup <- as.data.frame(biblio_coupling(refs_long, source = "citing", ref = "cited",
                                          normalized_weight_only = FALSE))
# citenets: coupling + cosine
cn_coup <- document_network(d_refs, "coupling", similarity = "cosine")

cat("=== biblionetwork ===\n")
print(bn_coup[, c("from", "to", "weight", "nb_shared_references")])
cat("\n=== citenets ===\n")
print(cn_coup)
```

### 8.6 All Five Normalization Formulas: citenets vs bibliometrix

```{r}
#| label: equiv-normalize
# Build a known co-occurrence matrix
A <- matrix(
  c(4,2,2,1, 2,3,2,2, 2,2,3,1, 1,2,1,2),
  nrow = 4, dimnames = list(paste0("R",1:4), paste0("R",1:4))
)

methods_map <- list(
  association = "association",
  cosine = "salton",
  jaccard = "jaccard",
  inclusion = "inclusion",
  equivalence = "equivalence"
)

results <- lapply(names(methods_map), function(m) {
  cn <- as.matrix(normalize(A, m))
  bm <- as.matrix(bibliometrix::normalizeSimilarity(
    Matrix::Matrix(A, sparse = TRUE), type = methods_map[[m]]
  ))
  bm[is.nan(bm)] <- 0; diag(bm) <- 0
  max_diff <- max(abs(cn - bm))
  data.frame(method = m, max_diff = max_diff,
             match = ifelse(max_diff < 1e-10, "EXACT", "DIFFERS"))
})
do.call(rbind, results)
```

### 8.7 Co-citation Cosine: citenets vs biblionetwork

```{r}
#| label: equiv-cocit
refs_long5 <- data.table(
  citing = rep(paste0("W", 1:5), each = 3),
  cited = c("R1","R2","R3", "R1","R2","R4", "R2","R3","R5",
            "R1","R3","R4", "R2","R5","R6")
)
d5 <- data.frame(id = paste0("W", 1:5), stringsAsFactors = FALSE)
d5$references <- list(
  c("R1","R2","R3"), c("R1","R2","R4"), c("R2","R3","R5"),
  c("R1","R3","R4"), c("R2","R5","R6")
)

bn_cc <- as.data.frame(biblio_cocitation(
  refs_long5, source = "citing", ref = "cited",
  normalized_weight_only = FALSE
))
cn_cc <- reference_network(d5, similarity = "cosine", threshold = 0)

cat("=== biblionetwork (co-citation cosine) ===\n")
print(bn_cc[, c("from", "to", "weight")])
cat("\n=== citenets (co-citation cosine) ===\n")
print(cn_cc[, c("from", "to", "weight")])
```

## 9. Counting Methods Compared Side by Side

```{r}
#| label: counting-comparison
# 10-paper dataset: compare all counting methods on co-authorship
methods_all <- c("full", "fractional", "paper",
                 "harmonic", "arithmetic", "geometric",
                 "adaptive_geometric", "golden")

comparison <- lapply(methods_all, function(m) {
  e <- author_network(biblio_data, "collaboration", counting = m)
  data.frame(
    counting = m,
    edges = nrow(e),
    total_weight = round(sum(e$weight), 3),
    max_weight = round(max(e$weight), 4),
    mean_weight = round(mean(e$weight), 4)
  )
})
do.call(rbind, comparison)
```

The total network weight reveals the fundamental difference between counting approaches: full counting inflates with team size, fractional normalizes per author, paper normalizes per paper.

## 10. Performance

```{r}
#| label: performance
# Benchmark on the example dataset (small, but demonstrates the pattern)
cat("Dataset:", nrow(biblio_data), "papers,",
    length(unique(unlist(biblio_data$authors))), "authors\n\n")

funs <- list(
  "author collab"    = function() author_network(biblio_data, "collaboration"),
  "author harmonic"  = function() author_network(biblio_data, "collaboration",
                                                  counting = "harmonic"),
  "ref co-citation"  = function() reference_network(biblio_data, threshold = 0),
  "doc coupling"     = function() document_network(biblio_data, "coupling"),
  "keyword co-occ"   = function() keyword_network(biblio_data, threshold = 0),
  "conetwork generic"= function() conetwork(biblio_data, "keywords", sep = NULL)
)

timings <- vapply(names(funs), function(nm) {
  system.time(funs[[nm]]())[3]
}, numeric(1))

data.frame(function_name = names(timings), seconds = round(timings, 4))
```

## 11. Quick Reference

### All Counting Methods

| Method | Type | Formula (author i of n) |
|--------|------|------------------------|
| `"full"` | Position-independent | 1 for all |
| `"fractional"` | Position-independent | 1/(n-1) per link |
| `"paper"` | Position-independent | 2/(n*(n-1)) per link |
| `"strength"` | Position-independent | IDF-weighted |
| `"harmonic"` | Position-dependent | (1/i) / H_n |
| `"arithmetic"` | Position-dependent | (n-i+1) / sum(1:n) |
| `"geometric"` | Position-dependent | 0.5^(i-1) normalized |
| `"adaptive_geometric"` | Position-dependent | r^(n-i), r=n^(1/(n-1)) |
| `"golden"` | Position-dependent | phi^(n-i) normalized |
| `"first"` | Special | First author = 1, rest = 0 |
| `"last"` | Special | Last author = 1, rest = 0 |
| `"first_last"` | Special | First + last elevated |
| `"position_weighted"` | Custom | User-defined vector |

### All Similarity Measures

| Similarity | Formula |
|------------|---------|
| `"none"` | Raw co-occurrence count |
| `"association"` | c_ij / (w_i * w_j) |
| `"cosine"` | c_ij / sqrt(w_i * w_j) |
| `"jaccard"` | c_ij / (w_i + w_j - c_ij) |
| `"inclusion"` | c_ij / min(w_i, w_j) |
| `"equivalence"` | c_ij^2 / (w_i * w_j) |

### All Network Functions

```r
# Entity networks (specialized)
author_network(data, type, counting, similarity, threshold, min_occur)
document_network(data, type, counting, similarity, threshold, min_occur)
reference_network(data, type, counting, similarity, threshold, min_occur)
keyword_network(data, field, counting, similarity, threshold, min_occur)
institution_network(data, type, counting, similarity, threshold, min_occur)
country_network(data, type, counting, similarity, threshold, min_occur)
source_network(data, type, counting, similarity, threshold, min_occur)

# Generic (any data frame)
conetwork(df, field, sep, by, aggregate, group)

# Readers
read_scopus(file)  read_wos(file)  read_openalex(data)
read_bibtex(file)  read_ris(file)  read_lens(file)

# Converters
to_igraph(edges)  to_tbl_graph(edges)  to_matrix(edges)

# Utils
normalize(matrix, method)  split_field(x, sep)
```

## References

- Batagelj, V., & Cerinsek, M. (2013). On bibliographic networks. *Scientometrics*, 96(3), 845--864.
- Hagen, N. T. (2008). Harmonic allocation of authorship credit. *Scientometrics*, 84(3), 785--793.
- Liu, W., & Fang, H. (2023). A geometric counting method adaptive to the author number. *Journal of Informetrics*, 17(2), 101397.
- Perianes-Rodriguez, A., Waltman, L., & van Eck, N. J. (2016). Constructing bibliometric networks: A comparison between full and fractional counting. *Journal of Informetrics*, 10(4), 1178--1195.
- Sen, S. K., & Gan, S. K. (1983). A mathematical extension of the idea of bibliographic coupling. *Annals of Library Science and Documentation*, 30(2), 78--82.
- Small, H. (1973). Co-citation in the scientific literature. *JASIS*, 24(4), 265--269.
- van Eck, N. J., & Waltman, L. (2009). How to normalize co-occurrence data? *JASIST*, 60(8), 1635--1651.
- Yan, E., & Ding, Y. (2012). Scholarly network similarities. *JASIST*, 63(7), 1313--1326.
